Exploring probability distributions for bivariate temporal granularities

### 2020-01-30 main.Rmd
changing cricket intro and figures - need updation of caption

cricket_tsibble_fld %>% 
  mutate(field = if_else(fielding_wckts==0, "no wickets", ">0 wickets")) %>% 
  #filter(fielding_wckts %in% c(0,1)) %>% 
  prob_plot( "field","over",
                               hierarchy_model,
                               response = "diff_run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("")

>>>>

cricket_tsibble_fld %>% 
  mutate(field = if_else(fielding_wckts==0, "no wickets", ">0 wickets")) %>% 
  #filter(fielding_wckts %in% c(0,1)) %>% 
  prob_plot( "field","over",
                               hierarchy_model,
                               response = "diff_run_rate",
                               plot_type = "boxplot",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("")
